---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

Plotly is a flexible framework for producing interactive graphics.

## Load `plotly` Library
```{r message = FALSE}
library(tidyverse)
library(p8105.datasets)

library(plotly)
```

## Initial data cleaning & subsetting
We are going to use Airbnb dataset for this lecture:
```{r}
data("nyc_airbnb")

nyc_airbnb =
  nyc_airbnb |>
  mutate(rating = review_scores_location / 2) |>
  select(rating, neighbourhood_group, neighbourhood,
         room_type, lat, long, price) |>
  drop_na(rating) |>
  filter(
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500
  )

```

## `plotly` Scatterplot
`text = ~text_label` includes desired information for each point in the scatterplot.
```{r}
nyc_airbnb |> 
  mutate(text_label = 
           str_c("Price: ", price, 
                 "\nNeighbourhood: ", neighbourhood)) |>
  plot_ly(
    x = ~lat, y = ~long, color = ~price, text = ~text_label,
    type = "scatter", mode = "markers", alpha = 0.5
  )
```

## `plotlib` Box plot 
```{r}
nyc_airbnb |>
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |>
  plot_ly(x = ~neighbourhood, y = ~price, color = ~neighbourhood,
          type = "box", colors = "viridis")
```

## `plotly` Bar chart 
```{r}
nyc_airbnb |>
  count(neighbourhood) |>
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) |>
  plot_ly(x = ~neighbourhood, y = ~n,
          type = "bar")
```

## `plotly` Other Graphs (from cheatsheet)
```{r}
plot_ly(z = volcano, type = "heatmap")
```

```{r}
plot_ly(
  type = "choropleth",
  locations = c("AZ", "CA", "VT"), 
  locationmode = "USA-states",
  colorscale = "viridis", 
  z = c( 10, 20, 40 )) |>
  layout(geo = list(scope = "usa"))
```

## `ggplotly`
Can convert a `ggplot` object straight to an interactive graphic using `ggplotly`. 

```{r}
scatter_ggplot = 
  nyc_airbnb |>
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = 0.25) +
  coord_cartesian()

ggplotly(scatter_ggplot)
```

## `flexdashboard`
To create dashboard:

* Can specify `flex_dashboard` as the output format in your R Markdown YAML.
* Can also use default dashboard: `File > New File > R Markdown > From Template`

Check `Dashboard` on the website or `flex_dashboard.RMD` for more information.


